\section{Reflection on Development Experience}

\subsection{Group Working}
It must to be admired that for such project a group of skilled people cooperating with each other is essential since too many different fields of programming and designing are involved. Also, it is important to make clear jobs each individual need to accomplish at the beginning of the project, which not only helps group members to focus on a particular part of works in the developing step, but also decreases the difficulty of later steps of the project such as combining and debugging.

Talking more with group members can help individuals since it is hard for oneself to discover the problems in the thinking or programming processes. We have experienced a lot that someone made silly mistakes but was not aware and other group members corrected it.

\subsection{Developing Tools}
Version control tools such as Github is necessary for group working because there exists many situation that multiple people working on same code files and conflicts may occur and be leaving unnoticeable. Such tools can compare the historical version of code files and highlight crucial parts for programmers to solve or automatically merge different copies of code.

\subsection{Scheduling}
Making a reasonable schedule for development and keep tight with it is significant for large projects. The schedule must give clear sub-deadlines for different tasks and flexibility should be left in advance for handling emergent issues, especially for CSE310's final project, which may conflict with a lot of other deadlines in the second semester of year-4.

Also, it is crucial for group members to have a clear and correct prediction on the total time consumption of the project, which helps them physically and mentally. It prevents them stay too late at night and have more relaxed mood when developing, which significantly reduces chances of producing unnoticeable bugs in code.